Minimizing post-shock forecasting error using disparate information

### 2020-06-28 manuscript/fig2.tex
revisions to data analysis

% Created by tikzDevice version 0.12.3 on 2020-06-11 18:44:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.29) -- (481.05, 90.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.21) -- (481.05, 86.29);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

### 2020-06-28 manuscript/manuscript.tex
revisions to data analysis

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.914$, $28.988$, and $26.444$, respectively. The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. Note that this parametric bootstrap procedure is conditioned  on the  donor pool. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. However, the risk-reduction quantities are inconsistent with the reality. The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.  It is consistent with the finding in Section \ref{parametricbootstrapsimulation} that voting for best estimator with estimated risk-reduction quantities is very likely to be inconsistent with the truth when the donor pool size $n$ is small.

@@

From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th. For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $1.657$, and $1.145$ dollars, respectively. These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. 
%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.  %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.

>>>>

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 1314.04.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is very similar to $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
    Leave-one-out consistency & 0.000 & 0.800 & 0.000
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap conditioned on the donor pool proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively. The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. Moreover, the leave-one-out consistency of the risk-reduction propositions are 0.000, 0.800, and 0.000 for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$, respectively. It implies that we should only use the propositions for $\hat{\alpha}_{\text{wadj}}$. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $3.924$, and $4.423$ dollars, respectively.
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. Moreover, the risk-reduction quantities are consistent with the reality as well. The results are also consistent with leave-one-out consistency for $\hat{\alpha}_{\text{wadj}}$ in that it  reduces the risk.

@@

From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th. For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $2.468$, and $1.145$ dollars, respectively. These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. 
%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.  %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.
